That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-22 ms.tex
new mcmc

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations from an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is FIXME. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

@@

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve. The best was $443  < X < 578$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.

>>>>

\begin{abstract}
    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet. Here we present a new analysis of the Hubble observations from an independent data reduction pipeline. We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality. The $3\,\sigma$ upper limit on the moon radius is $3.5R_\oplus$. FIXME: why are we different from TK18?  We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
\end{abstract}

@@

To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian. The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.  To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.  We then created an extraction box centered on the spectral trace. We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.  The best was $445  < X < 569$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.
